Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-07-06 paper/lostanlenRelevanceScattering.tex
masker tone -> masking tone

\subsection{Gammatone wavelets}
\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figures/gammatones}
\caption{
\label{fig:gammatones}
Gammatone wavelets $\psi(t)$ in the time domain with quality factors (a) $Q = 4$ and (b) $Q = 1$.
Oscillations (red, blue) are the real and imaginary parts. The envelope (yellow) is the complex modulus.}
\end{center}
\end{figure}
Wavelets
$\boldsymbol{\psi_{\gamma_1}}(t)$ and $\boldsymbol{\psi_{\gamma_2}}(t)$ are designed as fourth-order Gammatone
wavelets with one vanishing moment~\cite{Venkitaraman2014}, and are shown in Figure~\ref{fig:gammatones}.
In the context of auditory scene analysis, the asymmetric envelopes of Gammatone wavelets are more biologically plausible than the symmetric, Gaussian envelopes of the more widely used Morlet wavelets.
Indeed, it allows to reproduce two important psychoacoustic effects in the mammalian cochlea: the asymmetry of temporal masking and the asymmetry of spectral masking~\cite{Fastl2007}.
The asymmetry of temporal masking is the fact that a masking noise has to be louder if placed after the onset of a stimulus rather than before.
Likewise, because critical bands are skewed towards higher frequencies, a masker tone has to be louder if it is above the stimulus in frequency rather than below.

>>>>

\subsection{Gammatone wavelets}
\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figures/gammatones}
\caption{
\label{fig:gammatones}
Gammatone wavelets $\psi(t)$ in the time domain with quality factors (a) $Q = 4$ and (b) $Q = 1$.
Oscillations (red, blue) are the real and imaginary parts. The envelope (yellow) is the complex modulus.}
\end{center}
\end{figure}
Wavelets
$\boldsymbol{\psi_{\gamma_1}}(t)$ and $\boldsymbol{\psi_{\gamma_2}}(t)$ are designed as fourth-order Gammatone
wavelets with one vanishing moment~\cite{Venkitaraman2014}, and are shown in Figure~\ref{fig:gammatones}.
In the context of auditory scene analysis, the asymmetric envelopes of Gammatone wavelets are more biologically plausible than the symmetric, Gaussian envelopes of the more widely used Morlet wavelets.
Indeed, it allows to reproduce two important psychoacoustic effects in the mammalian cochlea: the asymmetry of temporal masking and the asymmetry of spectral masking~\cite{Fastl2007}.
The asymmetry of temporal masking is the fact that a masking noise has to be louder if placed after the onset of a stimulus rather than before.
Likewise, because critical bands are skewed towards higher frequencies, a masking tone has to be louder if it is above the stimulus in frequency rather than below.
